---
title: "Statistical analysis"
format:
  html:
    minimal: true
    code-copy: true
---

# Load packages

```{r}
pacman::p_load(
  rio,
  here,
  tidyverse,
  finalfit,
  gtsummary,
  flextable,
  geepack,
  broom,
  car,
  readr,
  survival,
  ggpubr,
  ggsci,
  ggstats,
  rfextras
)

# Run all scripts
rfextras::load_scripts()
```

# Import data

```{r}
# Data
data_factors <- rio::import(here("data", "data_factors.csv"))

# Attitudes
attitudes_data <- rio::import(here("data", "attitudes.csv"))

# Knowledges
knowledges_data <- rio::import(here("data", "knowledges.csv"))

# Practices
practices_data <- rio::import(here("data", "practices.csv"))
```

# Set theme and language

```{r}
# Set a gtsummary theme
gtsummary::theme_gtsummary_compact()
gtsummary::theme_gtsummary_journal(journal = "nejm")

# Set a gtsummary language
gtsummary::theme_gtsummary_language(language = "en")
```

# Process data

## Variable selection

```{r}
data_factors_1 <-
  data_factors_0 |>
  dplyr::select(
    # Demographics
    edad,
    edad.c,
    procedencia,
    etnia,
    religion,
    n_educacion,
    e_marital,
    ocupacion,
    ocupacion_convi,
    antec_fam,
    # Sexual and reproductive variables
    edad_relacion_sexual.c,
    parejas_sex.c,
    num_hijos.c,
    met_anticoncep,
    antec_ets,
    # Need review
    conocimiento,
    conocimiento_dico,
    actitud,
    practica
  )
```

# Outputs

## Figure S1: Barplot of knowledge, attitudes, and practices

```{r}
# Data
data_barplot <- data_factors_1 |>
  dplyr::select(conocimiento, actitud, practica) |>
  tidyr::pivot_longer(cols = everything(), names_to = "variable", values_to = "value") |>
  dplyr::group_by(variable, value) |>
  dplyr::summarise(n = n()) |>
  dplyr::mutate(prop = n / sum(n)) |>
  dplyr::mutate(percentage = round(prop * 100, 1))

# Plot
figure_s1 <- ggplot2::ggplot(data_barplot, aes(x = variable, y = percentage, fill = value)) +
  ggplot2::geom_bar(stat = 'identity') +
  ggplot2::geom_text(aes(label = paste0(percentage, "%")), position = position_stack(vjust = 0.5)) +
  ggplot2::scale_x_discrete(labels = c("Knowledge", "Attitude", "Practices")) +
  ggplot2::labs(y = "Percentage", x = element_blank(), fill = "Legend") +
  ggpubr::theme_pubr() +
  ggplot2::theme(legend.position = "right") +
  ggplot2::scale_fill_brewer(palette = "RdYlBu")

# View
figure_s1
```

## Figure S2: Likert plot of attitudes

```{r}
ggstats::gglikert(attitudes, labels_accuracy = .1, labels_hide_below = .2)
```

## Figure S3: Likert plot of practices

```{r}
ggstats::gglikert(practices, labels_accuracy = .1, labels_hide_below = .2)
```

## Figure S4: Likert plot of knowledges

```{r}
ggstats::gglikert(knowledges, labels_accuracy = .1, labels_hide_below = .2)
```

## Table 1: Characteristics

```{r}
table_1.1 <-
  data_factors_1 |>
  tbl_summary(include = c(edad:antec_fam)) |>
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})")

table_1.2 <-
  data_factors_1 |>
  tbl_summary(include = c(edad_relacion_sexual.c:antec_ets)) |>
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})")

table_1 <-
  tbl_stack(
    list(table_1.1, table_1.2),
    group_header = c("Demographics", "Reproductive and sexual characteristics")
  ) |>
  modify_caption("**Table 1**. Characteristics of the surveyed women")

# View
table_1
```

```{r}
table_1 <- as_flex_table(table_1)
# Save tables
save_as_docx(table_1, path = "Table_1.docx", align = "center")
```

## Table 1s. with three categories of level of knowledge

```{r}
table_1.1.s <-
  data_factors_1 |>
  tbl_summary(include = c(edad:antec_fam),
              by = conocimiento) |>
  add_p(test.args = all_tests("fisher.test") ~ list(simulate.p.value = TRUE)) |>  
  bold_p(t=0.05) |> 
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})") |> 
  modify_spanning_header(all_stat_cols(stat_0 = FALSE) ~ "**Level of knowledge**")

table_1.1.s <-
  data_factors_1 |>
  tbl_summary(include = c(edad_relacion_sexual.c:antec_ets),
              by = conocimiento) |>
  add_p(test.args = all_tests("fisher.test") ~ list(simulate.p.value = TRUE)) |>  
  bold_p(t=0.05) |> 
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})") 

table_1s <-
  tbl_stack(
    list(table_2.1, table_2.2),
    group_header = c(
      "Demographics",
      "Reproductive and sexual characteristics"
    )
  ) |>
  modify_caption(
    "**Table 2**. Bivariate analysis of the characteristics of the surveyed women")

```

```{r}
table_2 <- as_flex_table(table_2.1)
# Save tables
save_as_docx(table_2.1, path = "Table_2.1.docx", align = "center")
```

## Table 2. Level of knowledge with two categories

```{r}
table_2.1 <-
  data_factors_1 |>
  tbl_summary(include = c(edad:antec_fam),
              by = conocimiento_dico) |>
  add_p(test.args = all_tests("fisher.test") ~ list(simulate.p.value = TRUE)) |>  
  bold_p(t=0.05) |> 
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})") |> 
  modify_spanning_header(all_stat_cols(stat_0 = FALSE) ~ "**Level of knowledge**")

table_2.2 <-
  data_factors_1 |>
  tbl_summary(include = c(edad_relacion_sexual.c:antec_ets),
              by = conocimiento_dico) |>
  add_p(test.args = all_tests("fisher.test") ~ list(simulate.p.value = TRUE)) |>  
  bold_p(t=0.05) |> 
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})") 

table_2 <-
  tbl_stack(
    list(table_2.1, table_2.2),
    group_header = c(
      "Demographics",
      "Reproductive and sexual characteristics"
    )
  ) |>
  modify_caption(
    "Table 2. Sociodemographic and reproductive related characteristics by level of knowledge among women in Ica, Peru")
```

```{r}
table_2 <- as_flex_table(table_2)
# Save tables
save_as_docx(table_2, path = "Table_2.docx", align = "center")
```

## Table 3. Attitudes

```{r}
table_3.1 <-
  data_factors_1 |>
  tbl_summary(include = c(edad:antec_fam),
              by = actitud) |>
  add_p(test.args = all_tests("fisher.test") ~ list(simulate.p.value = TRUE)) |>  
  bold_p(t = 0.05) |> 
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})") |> 
  modify_spanning_header(all_stat_cols(stat_0 = FALSE) ~ "**Attitudes toward cervix cancer**")

table_3.2 <-
  data_factors_1 |>
  tbl_summary(include = c(edad_relacion_sexual.c:antec_ets),
              by = actitud) |>
  add_p(test.args = all_tests("fisher.test") ~ list(simulate.p.value = TRUE)) |>  
  bold_p(t = 0.05) |> 
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})") 

table_3 <-
  tbl_stack(
    list(table_3.1, table_3.2),
    group_header = c(
      "Demographics",
      "Reproductive and sexual characteristics"
    )
  ) |>
  modify_caption(
    "Table 3. Sociodemographic and reproductive related characteristics by attitudes among women in Ica, Peru")
```

```{r}
table_3 <- as_flex_table(table_3)
# Save tables
save_as_docx(table_3, path = "Table_3.docx", align = "center")
```

## Table 4. Practices

```{r}
table_4.1 <-
  data_factors_1 |>
  tbl_summary(include = c(edad:antec_fam),
              by = practica) |>
  add_p(test.args = all_tests("fisher.test") ~ list(simulate.p.value = TRUE)) |>  
  bold_p(t=0.05) |> 
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})") |> 
  modify_spanning_header(all_stat_cols(stat_0 = FALSE) ~ "**Practices regarding cervix cancer**")

table_4.2 <-
  data_factors_1 |>
  tbl_summary(include = c(edad_relacion_sexual.c:antec_ets),
              by = practica) |>
  add_p(test.args = all_tests("fisher.test") ~ list(simulate.p.value = TRUE)) |>  
  bold_p(t=0.05) |> 
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})") 

table_4 <-
  tbl_stack(
    list(table_4.1, table_4.2),
    group_header = c(
      "Demographics",
      "Reproductive and sexual characteristics"
    )
  ) |>
  modify_caption(
    "**Table 4**. Sociodemographic and reproductive related characteristics by practice among surveyed women in Ica, Peru")
```

```{r}
table_4 <- as_flex_table(table_4)
# Save tables
save_as_docx(table_4, path = "Table_4.docx", align = "center")
```

## Logistic regression analysis

### Variables selection for univariate logistic regression

```{r}
data_uv = 
  data_factors_1 |> 
  select(
    edad.c:antec_ets,
    conocimiento_dico,
    actitud,
    practica
  )
```

### Table 5. Variables that contribute to high knowledge

```{r}
tabla_5.1 <- data_uv |>
  tbl_uvregression(
    include = c(edad.c,
                etnia,
                n_educacion,
                e_marital,
                ocupacion,
                ocupacion_convi,
                antec_fam,
                edad_relacion_sexual.c,
                parejas_sex.c,
                num_hijos.c,
                met_anticoncep
                ),
    y = conocimiento_dico,
    method = glm,
    method.args = list(family = binomial(link = "logit")),
    exponentiate = TRUE,
    conf.int = TRUE,
    hide_n = TRUE,
    add_estimate_to_reference_rows = FALSE,
    pvalue_fun = ~ style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 2)
  ) |>
  bold_labels() |>
  bold_p(t = 0.05) |>
  modify_header(estimate = "**OR**", p.value = "**P value**")
```

```{r}
tabla_5.2 <- glm(
  conocimiento_dico ~
    edad.c + etnia + n_educacion + e_marital + ocupacion + ocupacion_convi + 
    antec_fam + edad_relacion_sexual.c + parejas_sex.c + num_hijos.c + 
    met_anticoncep,
  data = data_uv,
  family = binomial(link = "logit") ) |>
  tbl_regression(
    exponentiate = TRUE,
    conf.int = TRUE,
    pvalue_fun = ~ style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 2)
  ) |>
  bold_p(t = 0.05) |>
  modify_header(estimate = "**OR**", 
                p.value = "**P value**")
```

### Merge tables

```{r}
table_5 =
  tbl_merge(tbls = 
              list(tabla_5.1, tabla_5.2), 
            tab_spanner = c("**Univariate analysis**",
                            "**Multivariate analysis**"))
```

```{r}
table_5 <- as_flex_table(table_5)
# Save tables
save_as_docx(table_5, path = "Table_5.docx", align = "center")
```

### Table 6. Variables that contribute to good attitudes

```{r}
tabla_6.1 <- data_uv |>
  tbl_uvregression(
    include = c(etnia,
                n_educacion,
                ocupacion,
                ocupacion_convi,
                antec_fam,
                edad_relacion_sexual.c,
                parejas_sex.c,
                num_hijos.c,
                met_anticoncep
                ),
    y = actitud,
    method = glm,
    method.args = list(family = binomial(link = "logit")),
    exponentiate = TRUE,
    conf.int = TRUE,
    hide_n = TRUE,
    add_estimate_to_reference_rows = FALSE,
    pvalue_fun = ~ style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 2)
  ) |>
  bold_labels() |>
  bold_p(t = 0.05) |>
  modify_header(estimate = "**OR**", p.value = "**P value**")
```

```{r}
tabla_6.2 <- glm(
  actitud ~ etnia + n_educacion + ocupacion + ocupacion_convi + antec_fam +
    edad_relacion_sexual.c + parejas_sex.c + num_hijos.c + met_anticoncep,
    data = data_uv,
  family = binomial(link = "logit") ) |>
  tbl_regression(
    exponentiate = TRUE,
    conf.int = TRUE,
    pvalue_fun = ~ style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 2)
  ) |>
  bold_p(t = 0.05) |>
  modify_header(estimate = "**OR**", 
                p.value = "**P value**")
```

### Merge tables

```{r}
table_6 =
  tbl_merge(tbls = 
              list(tabla_6.1, tabla_6.2), 
            tab_spanner = c("**Univariate analysis**",
                            "**Multivariate analysis**"))
```

```{r}
table_6 <- as_flex_table(table_6)
# Save tables
save_as_docx(table_6, path = "Table_6.docx", align = "center")
```

### Table 7. Variables that contribute to good practices

```{r}
tabla_7.1 <- data_uv |>
  tbl_uvregression(
    include = c(edad.c,
                e_marital,
                ocupacion_convi,
                edad_relacion_sexual.c,
                num_hijos.c,
                ),
    y = practica,
    method = glm,
    method.args = list(family = binomial(link = "logit")),
    exponentiate = TRUE,
    conf.int = TRUE,
    hide_n = TRUE,
    add_estimate_to_reference_rows = FALSE,
    pvalue_fun = ~ style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 2)
  ) |>
  bold_labels() |>
  bold_p(t = 0.05) |>
  modify_header(estimate = "**OR**", p.value = "**P value**")
```

```{r}
tabla_7.2 <- glm(
  practica ~ edad.c + e_marital + ocupacion_convi + edad_relacion_sexual.c +
    num_hijos.c,
  data = data_uv,
  family = binomial(link = "logit") ) |>
  tbl_regression(
    exponentiate = TRUE,
    conf.int = TRUE,
    pvalue_fun = ~ style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 2)
  ) |>
  bold_p(t = 0.05) |>
  modify_header(estimate = "**OR**", 
                p.value = "**P value**")
```

### Merge tables

```{r}
table_7 =
  tbl_merge(tbls = 
              list(tabla_7.1, tabla_7.2), 
            tab_spanner = c("**Univariate analysis**",
                            "**Multivariate analysis**"))
```

```{r}
table_7 <- as_flex_table(table_7)
# Save tables
save_as_docx(table_7, path = "Table_7.docx", align = "center")
```

# Save outputs

