---
title: "Statistical analysis"
format:
  html:
    minimal: true
    code-copy: true
execute:
  warning: true
  message: true
---

# Load packages

```{r}
pacman::p_load(
  rio,
  here,
  tidyverse,
  finalfit,
  gtsummary,
  flextable,
  geepack,
  broom,
  car,
  readr,
  survival,
  ggpubr,
  ggsci,
  ggstats,
  bstfun,
  MASS,
  epiDisplay
)
```

# Import data

```{r}
# Data
data_factors <- rio::import(here("data", "data_factors.csv"))

# Attitudes
attitudes_data <- rio::import(here("data", "attitudes.csv"))

# Knowledges
knowledges_data <- rio::import(here("data", "knowledges.csv"))

# Practices
practices_data <- rio::import(here("data", "practices.csv"))
```

# Set theme and language

```{r}
# Set a gtsummary theme
gtsummary::theme_gtsummary_compact()
gtsummary::theme_gtsummary_journal(journal = "jama")

# Set a gtsummary language
gtsummary::theme_gtsummary_language(language = "en")
```

# Process data

## Setting variables

```{r}
source(here::here("scripts", "dictionary.R"))
```

## Variable selection

```{r}
data_factors_1 <-
  data_factors_0 |>
  dplyr::select(
    # Demographics
    edad,
    edad.c,
    procedencia,
    etnia,
    religion,
    n_educacion,
    e_marital,
    ocupacion,
    ocupacion_convi,
    antec_fam,
    # Sexual and reproductive variables
    edad_relacion_sexual.c,
    parejas_sex.c,
    num_hijos.c,
    met_anticoncep,
    antec_ets,
    # Need review
    conocimiento,
    conocimiento_dico,
    actitud,
    practica
  )
```

# Outputs

## Figure S1: Barplot of knowledge, attitudes, and practices

```{r fig.align='center'}
# Data
data_barplot <- data_factors_1 |>
  dplyr::select(conocimiento, actitud, practica) |>
  tidyr::pivot_longer(cols = everything(), names_to = "variable", values_to = "value") |>
  dplyr::group_by(variable, value) |>
  dplyr::summarise(n = n()) |>
  dplyr::mutate(prop = n / sum(n)) |>
  dplyr::mutate(percentage = round(prop * 100, 1))

# Plot
figure_s1 <- ggplot2::ggplot(data_barplot, aes(x = variable, y = percentage, fill = value)) +
  ggplot2::geom_bar(stat = 'identity') +
  ggplot2::geom_text(aes(label = paste0(percentage, "%")), position = position_stack(vjust = 0.5)) +
  ggplot2::scale_x_discrete(labels = c("Knowledge", "Attitude", "Practices")) +
  ggplot2::labs(y = "Percentage", x = element_blank(), fill = "Legend") +
  ggpubr::theme_pubr() +
  ggplot2::theme(legend.position = "right") +
  ggplot2::scale_fill_brewer(palette = "RdYlBu")

# View
figure_s1
```

## Figure S2: Likertplot of knowledges

```{r fig.align='center'}
# Likertplot
figure_s2 <-ggstats::gglikert(knowledges, labels_accuracy = .1, labels_hide_below = .2)

# View
figure_s2
```

## Figure S3: Likert plot of attitudes

```{r fig.align='center'}
# Likertplot
figure_s3 <- ggstats::gglikert(attitudes, labels_accuracy = .1, labels_hide_below = .2)

# View
figure_s3
```

## Figure S4: Likert plot of practices

```{r fig.align='center'}
# Liker plot
figure_s4 <- ggstats::gglikert(practices, labels_accuracy = .1, labels_hide_below = .2) +
  scale_fill_manual(values = c("#d8b365", "#5ab4ac"))

# View
figure_s4
```

## Table 1: Characteristics

```{r}
# Demographic characteristics
table_1.1 <-
  data_factors_1 |>
  tbl_summary(include = c(edad:antec_fam)) |>
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})")

# Reproductive and sexual characteristics
table_1.2 <-
  data_factors_1 |>
  tbl_summary(include = c(edad_relacion_sexual.c:antec_ets)) |>
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})")

# Stack tables
table_1 <-
  tbl_stack(
    list(table_1.1, table_1.2),
    group_header = c("Demographics", "Reproductive and sexual")
  ) |>
  modify_caption("**Table 1**. Characteristics of women surveyed")

# View
table_1
```

## Table S1. Characteristics by level of knowledge

```{r}
# Demographic characteristics
table_S1.1 <-
  data_factors_1 |>
  tbl_summary(
    include = c(edad:antec_fam), 
    by = conocimiento,
    statistic = list(
      all_continuous() ~ "{median} ({p25}, {p75})", 
      all_categorical() ~ "{n} ({p}%)"),
    digits = list(
      all_continuous() ~ c(1, 1), 
      all_categorical() ~ c(0, 1))) |>
  add_p(test.args = all_tests("fisher.test") ~ list(simulate.p.value = TRUE)) |>
  add_q(method = "holm") |>
  bold_p(t = 0.05) |>
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})") |>
  modify_spanning_header(all_stat_cols() ~ "**Knowledge of cervical cancer**") |>
  modify_footnote(all_stat_cols() ~ NA) |>
  modify_header(q.value = "**Adjusted p-value**")

# Reproductive and sexual characteristics
table_S1.2 <-
  data_factors_1 |>
  tbl_summary(
    include = c(edad_relacion_sexual.c:antec_ets), 
    by = conocimiento,
    statistic = list(
      all_continuous() ~ "{median} ({p25}, {p75})", 
      all_categorical() ~ "{n} ({p}%)"),
    digits = list(
      all_continuous() ~ c(1, 1), 
      all_categorical() ~ c(0, 1))) |>
  add_p(test.args = all_tests("fisher.test") ~ list(simulate.p.value = TRUE)) |>
  add_q(method = "holm") |>
  bold_p(t = 0.05) |>
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})") |>
  modify_footnote(all_stat_cols() ~ NA) |>
  modify_header(q.value = "**Adjusted p-value**")

# Stack tables
table_S1 <-
  tbl_stack(
    list(table_S1.1, table_S1.2),
    group_header = c("Demographics", "Reproductive and sexual")
  ) |>
  modify_caption("**Table S1**. Characteristics of women surveyed by level of knowledge")

# View
table_S1 
```

## Table S2. Characteristics by level of knowledge (two categories)

```{r}
# Demographic characteristics
table_S2.1 <-
  data_factors_1 |>
  tbl_summary(
    include = c(edad:antec_fam),
    by = conocimiento_dico,
    statistic = list(
      all_continuous() ~ "{median} ({p25}, {p75})", 
      all_categorical() ~ "{n} ({p}%)"),
    digits = list(
      all_continuous() ~ c(1, 1), 
      all_categorical() ~ c(0, 1))) |>
  add_p() |>  
  bold_p(t=0.05) |> 
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})") |> 
  modify_spanning_header(all_stat_cols() ~ "**Knowledge of cervical cancer**") |>
  modify_footnote(all_stat_cols() ~ NA)

# Reproductive and sexual characteristics
table_S2.2 <-
  data_factors_1 |>
  tbl_summary(
    include = c(edad_relacion_sexual.c:antec_ets),
    by = conocimiento_dico,
    statistic = list(
      all_continuous() ~ "{median} ({p25}, {p75})", 
      all_categorical() ~ "{n} ({p}%)"),
    digits = list(
      all_continuous() ~ c(1, 1), 
      all_categorical() ~ c(0, 1))) |>
  add_p() |>
  bold_p(t = 0.05) |>
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})") |>
  modify_footnote(all_stat_cols() ~ NA)

# Stack tables
table_S2 <-
  tbl_stack(
    list(table_S2.1, table_S2.2),
    group_header = c("Demographics", "Reproductive and sexual")
  ) |>
  modify_caption(
    "**Table S2**. Characteristics of women surveyed by level of knowledge (two categories)")

# View
table_S2
```

## Table S3. Characteristics by level of attitudes

```{r}
# Demographic characteristics
table_S3.1 <-
  data_factors_1 |>
  tbl_summary(
    include = c(edad:antec_fam),
    by = actitud,
    statistic = list(
      all_continuous() ~ "{median} ({p25}, {p75})", 
      all_categorical() ~ "{n} ({p}%)"),
    digits = list(
      all_continuous() ~ c(1, 1), 
      all_categorical() ~ c(0, 1))) |>
  add_p() |>  
  bold_p(t=0.05) |> 
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})") |> 
  modify_spanning_header(all_stat_cols() ~ "**Attitudes toward cervix cancer**") |>
  modify_footnote(all_stat_cols() ~ NA)

# Reproductive and sexual characteristics
table_S3.2 <-
  data_factors_1 |>
  tbl_summary(
    include = c(edad_relacion_sexual.c:antec_ets),
    by = actitud,
    statistic = list(
      all_continuous() ~ "{median} ({p25}, {p75})", 
      all_categorical() ~ "{n} ({p}%)"),
    digits = list(
      all_continuous() ~ c(1, 1), 
      all_categorical() ~ c(0, 1))) |>
  add_p() |>
  bold_p(t = 0.05) |>
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})") |>
  modify_footnote(all_stat_cols() ~ NA)

# Stack tables
table_S3 <-
  tbl_stack(
    list(table_S3.1, table_S3.2),
    group_header = c("Demographics", "Reproductive and sexual")
  ) |>
  modify_caption(
    "Table S3. Characteristics of women surveyed by level of attitudes")

# View
table_S3
```

## Table S4. Characteristics by level of practices

```{r}
# Demographic characteristics
table_S4.1 <-
  data_factors_1 |>
  tbl_summary(
    include = c(edad:antec_fam),
    by = practica,
    statistic = list(
      all_continuous() ~ "{median} ({p25}, {p75})", 
      all_categorical() ~ "{n} ({p}%)"),
    digits = list(
      all_continuous() ~ c(1, 1), 
      all_categorical() ~ c(0, 1))) |>
  add_p() |>  
  bold_p(t=0.05) |> 
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})") |> 
  modify_spanning_header(all_stat_cols() ~ "**Practices regarding cervix cancer**") |>
  modify_footnote(all_stat_cols() ~ NA)

# Reproductive and sexual characteristics
table_S4.2 <-
  data_factors_1 |>
  tbl_summary(
    include = c(edad_relacion_sexual.c:antec_ets),
    by = practica,
    statistic = list(
      all_continuous() ~ "{median} ({p25}, {p75})", 
      all_categorical() ~ "{n} ({p}%)"),
    digits = list(
      all_continuous() ~ c(1, 1), 
      all_categorical() ~ c(0, 1))) |>
  add_p() |>  
  bold_p(t=0.05) |> 
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})") |>
  modify_footnote(all_stat_cols() ~ NA)

# stack tables
table_S4 <-
  tbl_stack(
    list(table_S4.1, table_S4.2),
    group_header = c("Demographics", "Reproductive and sexual")
  ) |>
  modify_caption(
    "**Table S4**. Characteristics of women surveyed by level of practices")

# View
table_S4
```

## Table S5:. Univariable logistic regression analysis

### Variables selection for univariate logistic regression

```{r}
data_uv <- 
  data_factors_1 |> 
  dplyr::select(
    edad.c:antec_ets,
    conocimiento_dico,
    actitud,
    practica
  )
```

### Univariable regression analysis

#### Knowledges

```{r}
table_S5.1 <- data_uv |>
  tbl_uvregression(
    include = c(
      edad.c,
      etnia,
      n_educacion,
      e_marital,
      ocupacion,
      ocupacion_convi,
      antec_fam,
      edad_relacion_sexual.c,
      parejas_sex.c,
      num_hijos.c,
      met_anticoncep
    ),
    y = conocimiento_dico,
    method = glm,
    method.args = list(family = binomial(link = "logit")),
    exponentiate = TRUE,
    conf.int = TRUE,
    hide_n = TRUE,
    tidy_fun = broom.helpers::tidy_parameters,
    add_estimate_to_reference_rows = FALSE,
    pvalue_fun = ~ style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 2)
  ) |>
  bold_p(t = 0.05)
```

#### Actitudes

```{r}
table_S5.2 <- data_uv |>
    tbl_uvregression(
    include = c(
      edad.c,
      etnia,
      n_educacion,
      e_marital,
      ocupacion,
      ocupacion_convi,
      antec_fam,
      edad_relacion_sexual.c,
      parejas_sex.c,
      num_hijos.c,
      met_anticoncep
    ),
    y = actitud,
    method = glm,
    method.args = list(family = binomial(link = "logit")),
    exponentiate = TRUE,
    conf.int = TRUE,
    hide_n = TRUE,
    tidy_fun = broom.helpers::tidy_parameters,
    add_estimate_to_reference_rows = FALSE,
    pvalue_fun = ~ style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 2)
  ) |>
  bold_p(t = 0.05)
```

#### Practices

```{r}
table_S5.3 <- data_uv |>
    tbl_uvregression(
    include = c(
      edad.c,
      etnia,
      n_educacion,
      e_marital,
      ocupacion,
      ocupacion_convi,
      antec_fam,
      edad_relacion_sexual.c,
      parejas_sex.c,
      num_hijos.c,
      met_anticoncep
    ),
    y = practica,
    method = glm,
    method.args = list(family = binomial(link = "logit")),
    exponentiate = TRUE,
    conf.int = TRUE,
    hide_n = TRUE,
    tidy_fun = broom.helpers::tidy_parameters,
    add_estimate_to_reference_rows = FALSE,
    pvalue_fun = ~ style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 2)
  ) |>
  bold_p(t = 0.05)
```

```{r}
# Merge tables
table_S5 <- tbl_merge(
  tbls =
    list(table_S5.1, table_S5.2, table_S5.3),
  tab_spanner = c("**Knowleges**", "**Attitudes**", "**Practices**")
)

# View
table_S5 
```

## Table 2. Knowledges multivariable regression analysis

### Multivariate full regression 

```{r fig.width = 9, fig.height = 9, fig.align='center'}
mv_reg_know <- glm(
  conocimiento_dico ~
    edad.c + etnia + n_educacion + e_marital + ocupacion + ocupacion_convi +
    antec_fam + edad_relacion_sexual.c + parejas_sex.c + num_hijos.c +
    met_anticoncep,
  family = binomial(link = "logit"),
  data = data_uv
)

# Summary with Wald and LRT p-values
epiDisplay::logistic.display(mv_reg_know, simplified = FALSE, crude = FALSE)

# Visual check of model assumptions
performance::check_model(mv_reg_know)

# Indices of model performance
performance::model_performance(mv_reg_know)

# Check for multicollinearity
performance::check_collinearity(mv_reg_know, ci = NULL)
```

### Stepwise regression

```{r}
mv_reg_know |>
  MASS::stepAIC(direction = "both", trace = FALSE)
```

### Multivariate reduced regression

```{r fig.width = 9, fig.height = 9, fig.align='center'}
step_mv_reg_know <- glm(
  conocimiento_dico ~ n_educacion + ocupacion_convi + antec_fam + 
    edad_relacion_sexual.c + met_anticoncep,
  family = binomial(link = "logit"),
  data = data_uv
)

# Summary with Wald and LRT p-values
epiDisplay::logistic.display(step_mv_reg_know, simplified = FALSE, crude = FALSE)

# Visual check of model assumptions
performance::check_model(step_mv_reg_know)

# Indices of model performance
performance::model_performance(step_mv_reg_know)

# Check for multicollinearity
performance::check_collinearity(step_mv_reg_know, ci = NULL)
```

### Comparison of models

```{r}
# Compare performance of different models
performance::compare_performance(mv_reg_know, step_mv_reg_know, verbose = TRUE)
# Radar plot to compare models
plot(performance::compare_performance(mv_reg_know, step_mv_reg_know, rank = TRUE, verbose = TRUE))

# Likelihood Ratio Test (LRT for comparison)
performance::test_likelihoodratio(step_mv_reg_know, mv_reg_know)
```

### Final table

```{r}
table_2  <- glm(
  conocimiento_dico ~ n_educacion + ocupacion_convi +
    antec_fam + edad_relacion_sexual.c + met_anticoncep,
  family = binomial(link = "logit"),
  data = data_uv
) |>
  tbl_regression(
    exponentiate = TRUE,
    conf.int = TRUE,
    pvalue_fun = ~ style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 2)
  ) |>
  bold_p(t = 0.05) |>
  bstfun::add_inline_forest_plot()

# View
table_2
```

## Table 3. Attitudes multivariable regression analysis

### Multivariate full regression 

```{r fig.width = 9, fig.height = 9, fig.align='center'}
mv_reg_atti <- glm(
  actitud ~
    edad.c + etnia + n_educacion + e_marital + ocupacion + ocupacion_convi +
    antec_fam + edad_relacion_sexual.c + parejas_sex.c + num_hijos.c +
    met_anticoncep,
  family = binomial(link = "logit"),
  data = data_uv,
)

# Summary with Wald and LRT p-values
epiDisplay::logistic.display(mv_reg_atti, simplified = FALSE, crude = FALSE)

# Visual check of model assumptions
performance::check_model(mv_reg_atti)

# Indices of model performance
performance::model_performance(mv_reg_atti)

# Check for multicollinearity
performance::check_collinearity(mv_reg_atti, ci = NULL)
```

### Stepwise regression

```{r}
mv_reg_atti |>
  MASS::stepAIC(direction = "both", trace = FALSE)
```

### Multivariate reduced regression

```{r fig.width = 9, fig.height = 9, fig.align='center'}
step_mv_reg_atti <- glm(
  actitud ~ n_educacion + ocupacion + edad_relacion_sexual.c + met_anticoncep,
  family = binomial(link = "logit"),
  data = data_uv
)

# Summary with Wald and LRT p-values
epiDisplay::logistic.display(step_mv_reg_atti, simplified = FALSE, crude = FALSE)

# Visual check of model assumptions
performance::check_model(step_mv_reg_atti)

# Indices of model performance
performance::model_performance(step_mv_reg_atti)

# Check for multicollinearity
performance::check_collinearity(step_mv_reg_atti, ci = NULL)
```

### Comparison of models

```{r}
# Compare performance of different models
performance::compare_performance(mv_reg_atti, step_mv_reg_atti, verbose = TRUE)
# Radar plot to compare models
plot(performance::compare_performance(mv_reg_atti, step_mv_reg_atti, rank = TRUE, verbose = TRUE))

# Likelihood Ratio Test (LRT for comparison)
performance::test_likelihoodratio(step_mv_reg_atti, mv_reg_atti)
```

### Final table

```{r}
table_3  <- glm(
  actitud ~ n_educacion + ocupacion + edad_relacion_sexual.c + met_anticoncep,
  family = binomial(link = "logit"),
  data = data_uv
) |>
  tbl_regression(
    exponentiate = TRUE,
    conf.int = TRUE,
    pvalue_fun = ~ style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 2)
  ) |>
  bold_p(t = 0.05) |>
  bstfun::add_inline_forest_plot()

# View
table_3
```

```{r}
tabla_6.2 <- glm(
  actitud ~ etnia + n_educacion + ocupacion + ocupacion_convi + antec_fam +
    edad_relacion_sexual.c + parejas_sex.c + num_hijos.c + met_anticoncep,
    data = data_uv,
  family = binomial(link = "logit") ) |>
  tbl_regression(
    exponentiate = TRUE,
    conf.int = TRUE,
    pvalue_fun = ~ style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 2)
  ) |>
  bold_p(t = 0.05) |>
  add_vif() |>
  modify_header(estimate = "**OR**", 
                p.value = "**P value**") |>
  bstfun::add_inline_forest_plot()
```

## Table 4. Practices multivariable regression analysis

### Multivariate full regression 

```{r fig.width = 9, fig.height = 9, fig.align='center'}
mv_reg_pract <- glm(
  practica ~
    edad.c + etnia + n_educacion + e_marital + ocupacion + ocupacion_convi +
    antec_fam + edad_relacion_sexual.c + parejas_sex.c + num_hijos.c +
    met_anticoncep,
  family = binomial(link = "logit"),
  data = data_uv,
)

# Summary with Wald and LRT p-values
epiDisplay::logistic.display(mv_reg_pract, simplified = FALSE, crude = FALSE)

# Visual check of model assumptions
performance::check_model(mv_reg_pract)

# Indices of model performance
performance::model_performance(mv_reg_pract)

# Check for multicollinearity
performance::check_collinearity(mv_reg_pract, ci = NULL)
```

### Stepwise regression

```{r}
mv_reg_pract |>
  MASS::stepAIC(direction = "both", trace = FALSE)
```

### Multivariate reduced regression

```{r fig.width = 9, fig.height = 9, fig.align='center'}
step_mv_reg_pract <- glm(
  practica ~ etnia + n_educacion + ocupacion + edad_relacion_sexual.c + num_hijos.c,
  family = binomial(link = "logit"),
  data = data_uv
)

# Summary with Wald and LRT p-values
epiDisplay::logistic.display(step_mv_reg_pract, simplified = FALSE, crude = FALSE)

# Visual check of model assumptions
performance::check_model(step_mv_reg_pract)

# Indices of model performance
performance::model_performance(step_mv_reg_pract)

# Check for multicollinearity
performance::check_collinearity(step_mv_reg_pract, ci = NULL)
```

### Comparison of models

```{r}
# Compare performance of different models
performance::compare_performance(mv_reg_pract, step_mv_reg_pract, verbose = TRUE)
# Radar plot to compare models
plot(performance::compare_performance(mv_reg_pract, step_mv_reg_pract, rank = TRUE, verbose = TRUE))

# Likelihood Ratio Test (LRT for comparison)
performance::test_likelihoodratio(step_mv_reg_pract, mv_reg_pract)
```
### Final table

```{r}
table_4 <- glm(
  practica ~ etnia + n_educacion + ocupacion + edad_relacion_sexual.c + num_hijos.c,
  family = binomial(link = "logit"),
  data = data_uv
) |>
  tbl_regression(
    exponentiate = TRUE,
    conf.int = TRUE,
    pvalue_fun = ~ style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 2)
  ) |>
  bold_p(t = 0.05)

# View
table_4
```

# Save outputs

## Tables

```{r}
# Save tables
flex_table_1 <- gtsummary::as_flex_table(table_1)
save_as_docx(
  flex_table_1,
  align = "center",
  path = here("outputs", "Table_1.docx"))

flex_table_S1 <- gtsummary::as_flex_table(table_S1)
save_as_docx(
  flex_table_S1,
  align = "center",
  path = here("outputs", "Table_S1.docx"))

flex_table_S2 <- gtsummary::as_flex_table(table_S2)
save_as_docx(
  flex_table_S2,
  align = "center",
  path = here("outputs", "Table_S2.docx"))

flex_table_S3 <- gtsummary::as_flex_table(table_S3)
save_as_docx(
  flex_table_S3,
  align = "center",
  path = here("outputs", "Table_S3.docx"))

flex_table_S4 <- gtsummary::as_flex_table(table_S4)
save_as_docx(
  flex_table_S4,
  align = "center",
  path = here("outputs", "Table_S4.docx"))

flex_table_S5 <- gtsummary::as_flex_table(table_S5)
save_as_docx(
  flex_table_S5,
  align = "center",
  path = here("outputs", "Table_S5.docx"))

flex_table_2 <- gtsummary::as_flex_table(table_2)
save_as_docx(
  flex_table_2,
  align = "center",
  path = here("outputs", "Table_2.docx"))

flex_table_3 <- gtsummary::as_flex_table(table_3)
save_as_docx(
  flex_table_3,
  align = "center",
  path = here("outputs", "Table_3.docx"))

flex_table_4 <- gtsummary::as_flex_table(table_4)
save_as_docx(
  flex_table_4,
  align = "center",
  path = here("outputs", "Table_4.docx"))
```

## Figures

```{r}
# Save figure S1 (JPEG)
ggsave(
  plot = figure_s2,
  filename = here("outputs", "FIG_S1.jpeg"),
  width = 9,
  height = 6,
  dpi = 500,
  units = "in")

# Save figure S2 (JPEG)
ggsave(
  plot = figure_s3,
  filename = here("outputs", "FIG_S2.jpeg"),
  width = 9,
  height = 6,
  dpi = 500,
  units = "in")

# Save figure S3 (JPEG)
ggsave(
  plot = figure_s4,
  filename = here("outputs", "FIG_S3.jpeg"),
  width = 9,
  height = 3,
  dpi = 500,
  units = "in")
```

