---
title: "Statistical analysis"
format:
  html:
    minimal: true
    code-copy: true
---

## Load packages

```{r}
pacman::p_load(
  here, 
  tidyverse, 
  finalfit, 
  gtsummary, 
  flextable, 
  geepack, 
  broom, 
  car, 
  readr, 
  survival, 
  ggpubr
)

```

## Import data

```{r}
data_factors <- read_delim(here("data", "data_factors.csv"), 
                            delim = ";", 
                            escape_double = FALSE, 
                            trim_ws = TRUE)
```

## Setting theme and language

```{r}
my_gtsummary_theme <-
  list(
    "pkgwide-fn:pvalue_fun" = function(x)
      style_pvalue(x, digits = 2),
    "pkgwide-fn:prependpvalue_fun" = function(x)
      style_pvalue(x, digits = 2, prepend_p = TRUE),
    "tbl_summary-str:continuous_stat" = "{median} ({p25}, {p75})",
    "tbl_summary-str:categorical_stat" = "{n} ({p}%)",
    "tbl_summary-fn:percent_fun" = function(x)
      style_number(x, digits = 1, scale = 100),
    "tbl_summary-arg:missing" = "no"
  )

set_gtsummary_theme(theme_gtsummary_compact(), 
                    my_gtsummary_theme)

theme_gtsummary_language(language = "en")
```

## Setting up variables

```{r}
data_factors_0 <-
  data_factors |>
  mutate(
    edad = ff_label(edad, "Age (years)"),
    edad.c = case_when(edad < 38 ~ "< 38", edad >= 38 &
                         edad <= 50 ~ "38-50", edad > 50 ~ "> 50") |>
      fct_relevel("< 38", "38-50", "> 50") |>
      ff_label("Age (years)"),
    
    e_marital = factor(e_marital) |> ###
      fct_recode(
        "Married" = "casada",
        "Cohabiting" = "conviviente",
        "Single" = "soltera",
        "Widowed" = "viuda"
      ) |>
      fct_relevel("Married", "Cohabiting", "Single", "Widowed") |>
      ff_label("Marital status"),
    
    n_educacion = factor(n_educacion) |> # Changed
      fct_recode(
        "Primary or Secundary" = "primaria",
        "Primary or Secundary" = "secundaria",
        "Higher than Secondary" = "superior"
      ) |>
      fct_relevel("Primary or Secundary", "Higher than Secondary") |>
      ff_label("Education level"),
    
    religion = factor(religion) |> ###
      fct_recode(
        "None" = "ninguna",
        "Catholic" = "catolico",
        "Evangelical" = "evangelista"
      ) |>
      fct_relevel("None", "Catholic", "Evangelical") |>
      ff_label("Religion"),
    
    etnia = factor(etnia) |> ###
      fct_recode(
        "Mestizo" = "mestizo",
        "White" = "blanco",
        "Other" = "otro"
      ) |>
      fct_relevel("Mestizo", "White", "Other") |>
      ff_label("Ethnicity"),
    
    procedencia = factor(procedencia) |> ###
      fct_recode("Urban" = "urbano", "Rural" = "rural") |>
      fct_relevel("Urban", "Rural") |>
      ff_label("Origin"),
    
    ocupacion = factor(ocupacion) |> ###
      fct_recode(
        "Student" = "estudiante",
        "Employed" = "empleada",
        "Homemaker" = "ama de casa",
        "Unemployed" = "sin empleo",
        "Other" = "otro",
      ) |>
      fct_relevel("Student", "Employed", "Homemaker", "Unemployed", "Other") |>
      ff_label("Occupation"),
    
    ocupacion_convi = factor(ocupacion_convi) |> ###
      fct_recode(
        "Student" = "estudiante",
        "Employed" = "empleado",
        "Unemployed" = "sin empleo",
        "Other" = "otro"
      ) |>
      fct_relevel("Student", "Employed", "Unemployed", "Other") |>
      ff_label("Partner's occupation"),
    
    antec_fam = factor(antec_fam) |> ###
      fct_recode("Yes" = "si", "No" = "no") |>
      fct_relevel("Yes", "No") |>
      ff_label("Family history"),
    
    edad_relacion_sexual.c = case_when(
      edad_relacion_sexual <= 18  ~ "18 or younger",
      edad_relacion_sexual >= 19 &
      edad_relacion_sexual <= 21 ~ "19-21",
      edad_relacion_sexual >= 22 ~ "22 or older"
      ) |>
      fct_relevel("18 or younger", "19-21", "22 or older") |>
      ff_label("Age at first sexual intercourse"),

    parejas_sex.c = case_when(
      parejas_sex <= 1 ~ "0 or 1",
      parejas_sex == 2 ~ "2",
      parejas_sex == 3 ~ "3",
      parejas_sex >= 4 ~ "4 or more"
    ) |>
      fct_relevel("0 or 1", "2", "3", "4 or more") |>
      ff_label("Number of sexual partners"),
    
    num_hijos.c = case_when( ### Changed
      num_hijos == 0 ~ "0",
      num_hijos == 1 ~ "1",
      num_hijos == 2 ~ "2",
      num_hijos >= 3 ~ "3 or more"
    ) |>
      fct_relevel("0", "1", "2", "3 or more") |>
      ff_label("Number of children"),

    met_anticoncep = factor(met_anticoncep) |> # Changed
      fct_recode(
        "Not using" = "no uso",
        "Oral contraceptives" = "aco",
        "Injection" = "ampolla de 3 meses",
        "Injection" = "ampolla mes",
        "IUD" = "diu",
        "Subdermal implant" = "implante_sd"
      )  |>
      fct_relevel(
        "Not using",
        "Oral contraceptives",
        "Injection",
        "IUD",
        "Subdermal implant"
      ) |>
      ff_label("Contraceptive method"),
    
    antec_ets = factor(antec_ets) |> ###
      fct_recode("Yes" = "si", "No" = "no") |>
      fct_relevel("Yes", "No") |>
      ff_label("History of STIs"),
    
    conocimiento = case_when(
      conocimiento == "no conoce" |
        conocimiento == "bajo" ~ "Low/No knowledge",
      conocimiento == "medio" ~ "Medium" ,
      TRUE ~ "High"
    ) |>
      fct_relevel("Low/No knowledge", "Medium", "High") |>
      ff_label("Knowledge level"),
    
    conocimiento_dico = case_when(
      conocimiento == "Low/No knowledge" |
        conocimiento == "medio" ~ "Medium to No knowledge",
      TRUE ~ "High"
    ) |>
      fct_relevel("Medium to No knowledge", "High") |>
      ff_label("Knowledge level"),
    
    actitud = case_when(actitud == "negativa" ~ "Negative", TRUE ~ "Positive") |>
      fct_relevel("Negative", "Positive") |>
      ff_label("Attitude"),
    
    practica = case_when(practica == "incorrecta" ~ "Incorrect", TRUE ~ "Correct") |>
      fct_relevel("Incorrect", "Correct") |>
      ff_label("Practices")
  )
```

## Selección de variables

```{r}
data_factors_1 = 
  data_factors_0 |>
  select(
    # Demographics
    edad,
    edad.c,
    procedencia,
    etnia,
    religion,
    n_educacion,
    e_marital,
    ocupacion,
    ocupacion_convi,
    antec_fam,
    # Sexual and reproductive variables
    edad_relacion_sexual.c,
    parejas_sex.c,
    num_hijos.c,
    met_anticoncep,
    antec_ets,
    #variables dependientes
    conocimiento, 
    conocimiento_dico,
    actitud,
    practica
  )
```

# Outputs

## Table 1

```{r}
table_1.1 <-
  data_factors_1 |>
  tbl_summary(include = c(edad:antec_fam)) |>
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})")

table_1.2 <-
  data_factors_1 |>
  tbl_summary(include = c(edad_relacion_sexual.c:antec_ets)) |>
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})")

table_1 <-
  tbl_stack(
    list(table_1.1, table_1.2),
    group_header = c(
      "Demographics",
      "Reproductive and sexual characteristics"
    )
  ) |>
  modify_caption(
    "**Table 1**. Characteristics of the surveyed women")

```

```{r}
table_1 <- as_flex_table(table_1)
# Save tables
save_as_docx(table_1, path = "Table_1.docx", align = "center")
```

## Table 1s. with three categories of level of knowledge

```{r}
table_1.1.s <-
  data_factors_1 |>
  tbl_summary(include = c(edad:antec_fam),
              by = conocimiento) |>
  add_p(test.args = all_tests("fisher.test") ~ list(simulate.p.value = TRUE)) |>  
  bold_p(t=0.05) |> 
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})") |> 
  modify_spanning_header(all_stat_cols(stat_0 = FALSE) ~ "**Level of knowledge**")

table_1.1.s <-
  data_factors_1 |>
  tbl_summary(include = c(edad_relacion_sexual.c:antec_ets),
              by = conocimiento) |>
  add_p(test.args = all_tests("fisher.test") ~ list(simulate.p.value = TRUE)) |>  
  bold_p(t=0.05) |> 
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})") 

table_1s <-
  tbl_stack(
    list(table_2.1, table_2.2),
    group_header = c(
      "Demographics",
      "Reproductive and sexual characteristics"
    )
  ) |>
  modify_caption(
    "**Table 2**. Bivariate analysis of the characteristics of the surveyed women")

```

```{r}
table_2 <- as_flex_table(table_2.1)
# Save tables
save_as_docx(table_2.1, path = "Table_2.1.docx", align = "center")
```

## Table 2. Level of knowledge with two categories

```{r}
table_2.1 <-
  data_factors_1 |>
  tbl_summary(include = c(edad:antec_fam),
              by = conocimiento_dico) |>
  add_p(test.args = all_tests("fisher.test") ~ list(simulate.p.value = TRUE)) |>  
  bold_p(t=0.05) |> 
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})") |> 
  modify_spanning_header(all_stat_cols(stat_0 = FALSE) ~ "**Level of knowledge**")

table_2.2 <-
  data_factors_1 |>
  tbl_summary(include = c(edad_relacion_sexual.c:antec_ets),
              by = conocimiento_dico) |>
  add_p(test.args = all_tests("fisher.test") ~ list(simulate.p.value = TRUE)) |>  
  bold_p(t=0.05) |> 
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})") 

table_2 <-
  tbl_stack(
    list(table_2.1, table_2.2),
    group_header = c(
      "Demographics",
      "Reproductive and sexual characteristics"
    )
  ) |>
  modify_caption(
    "Table 2. Sociodemographic and reproductive related characteristics by level of knowledge among women in Ica, Peru")
```

```{r}
table_2 <- as_flex_table(table_2)
# Save tables
save_as_docx(table_2, path = "Table_2.docx", align = "center")
```

## Table 3. Attitudes

```{r}
table_3.1 <-
  data_factors_1 |>
  tbl_summary(include = c(edad:antec_fam),
              by = actitud) |>
  add_p(test.args = all_tests("fisher.test") ~ list(simulate.p.value = TRUE)) |>  
  bold_p(t = 0.05) |> 
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})") |> 
  modify_spanning_header(all_stat_cols(stat_0 = FALSE) ~ "**Attitudes toward cervix cancer**")

table_3.2 <-
  data_factors_1 |>
  tbl_summary(include = c(edad_relacion_sexual.c:antec_ets),
              by = actitud) |>
  add_p(test.args = all_tests("fisher.test") ~ list(simulate.p.value = TRUE)) |>  
  bold_p(t = 0.05) |> 
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})") 

table_3 <-
  tbl_stack(
    list(table_3.1, table_3.2),
    group_header = c(
      "Demographics",
      "Reproductive and sexual characteristics"
    )
  ) |>
  modify_caption(
    "Table 3. Sociodemographic and reproductive related characteristics by attitudes among women in Ica, Peru")
```

```{r}
table_3 <- as_flex_table(table_3)
# Save tables
save_as_docx(table_3, path = "Table_3.docx", align = "center")
```

## Table 4. Practices

```{r}
table_4.1 <-
  data_factors_1 |>
  tbl_summary(include = c(edad:antec_fam),
              by = practica) |>
  add_p(test.args = all_tests("fisher.test") ~ list(simulate.p.value = TRUE)) |>  
  bold_p(t=0.05) |> 
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})") |> 
  modify_spanning_header(all_stat_cols(stat_0 = FALSE) ~ "**Practices regarding cervix cancer**")

table_4.2 <-
  data_factors_1 |>
  tbl_summary(include = c(edad_relacion_sexual.c:antec_ets),
              by = practica) |>
  add_p(test.args = all_tests("fisher.test") ~ list(simulate.p.value = TRUE)) |>  
  bold_p(t=0.05) |> 
  modify_header(all_stat_cols() ~ "**{level}**, (n = {n})") 

table_4 <-
  tbl_stack(
    list(table_4.1, table_4.2),
    group_header = c(
      "Demographics",
      "Reproductive and sexual characteristics"
    )
  ) |>
  modify_caption(
    "**Table 4**. Sociodemographic and reproductive related characteristics by practice among surveyed women in Ica, Peru")
```

```{r}
table_4 <- as_flex_table(table_4)
# Save tables
save_as_docx(table_4, path = "Table_4.docx", align = "center")
```

## Logistic regression analysis

### Variables selection for univariate logistic regression

```{r}
data_uv = 
  data_factors_1 |> 
  select(
    edad.c:antec_ets,
    conocimiento_dico,
    actitud,
    practica
  )
```

### Table 5. Variables that contribute to high knowledge

```{r}
tabla_5.1 <- data_uv |>
  tbl_uvregression(
    include = c(edad.c,
                etnia,
                n_educacion,
                e_marital,
                ocupacion,
                ocupacion_convi,
                antec_fam,
                edad_relacion_sexual.c,
                parejas_sex.c,
                num_hijos.c,
                met_anticoncep
                ),
    y = conocimiento_dico,
    method = glm,
    method.args = list(family = binomial(link = "logit")),
    exponentiate = TRUE,
    conf.int = TRUE,
    hide_n = TRUE,
    add_estimate_to_reference_rows = FALSE,
    pvalue_fun = ~ style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 2)
  ) |>
  bold_labels() |>
  bold_p(t = 0.05) |>
  modify_header(estimate = "**OR**", p.value = "**P value**")
```

```{r}
tabla_5.2 <- glm(
  conocimiento_dico ~
    edad.c + etnia + n_educacion + e_marital + ocupacion + ocupacion_convi + 
    antec_fam + edad_relacion_sexual.c + parejas_sex.c + num_hijos.c + 
    met_anticoncep,
  data = data_uv,
  family = binomial(link = "logit") ) |>
  tbl_regression(
    exponentiate = TRUE,
    conf.int = TRUE,
    pvalue_fun = ~ style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 2)
  ) |>
  bold_p(t = 0.05) |>
  modify_header(estimate = "**OR**", 
                p.value = "**P value**")
```

### Merge tables

```{r}
table_5 =
  tbl_merge(tbls = 
              list(tabla_5.1, tabla_5.2), 
            tab_spanner = c("**Univariate analysis**",
                            "**Multivariate analysis**"))
```

```{r}
table_5 <- as_flex_table(table_5)
# Save tables
save_as_docx(table_5, path = "Table_5.docx", align = "center")
```

### Table 6. Variables that contribute to good attitudes

```{r}
tabla_6.1 <- data_uv |>
  tbl_uvregression(
    include = c(etnia,
                n_educacion,
                ocupacion,
                ocupacion_convi,
                antec_fam,
                edad_relacion_sexual.c,
                parejas_sex.c,
                num_hijos.c,
                met_anticoncep
                ),
    y = actitud,
    method = glm,
    method.args = list(family = binomial(link = "logit")),
    exponentiate = TRUE,
    conf.int = TRUE,
    hide_n = TRUE,
    add_estimate_to_reference_rows = FALSE,
    pvalue_fun = ~ style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 2)
  ) |>
  bold_labels() |>
  bold_p(t = 0.05) |>
  modify_header(estimate = "**OR**", p.value = "**P value**")
```

```{r}
tabla_6.2 <- glm(
  actitud ~ etnia + n_educacion + ocupacion + ocupacion_convi + antec_fam +
    edad_relacion_sexual.c + parejas_sex.c + num_hijos.c + met_anticoncep,
    data = data_uv,
  family = binomial(link = "logit") ) |>
  tbl_regression(
    exponentiate = TRUE,
    conf.int = TRUE,
    pvalue_fun = ~ style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 2)
  ) |>
  bold_p(t = 0.05) |>
  modify_header(estimate = "**OR**", 
                p.value = "**P value**")
```

### Merge tables

```{r}
table_6 =
  tbl_merge(tbls = 
              list(tabla_6.1, tabla_6.2), 
            tab_spanner = c("**Univariate analysis**",
                            "**Multivariate analysis**"))
```

```{r}
table_6 <- as_flex_table(table_6)
# Save tables
save_as_docx(table_6, path = "Table_6.docx", align = "center")
```

### Table 7. Variables that contribute to good practices

```{r}
tabla_7.1 <- data_uv |>
  tbl_uvregression(
    include = c(edad.c,
                e_marital,
                ocupacion_convi,
                edad_relacion_sexual.c,
                num_hijos.c,
                ),
    y = practica,
    method = glm,
    method.args = list(family = binomial(link = "logit")),
    exponentiate = TRUE,
    conf.int = TRUE,
    hide_n = TRUE,
    add_estimate_to_reference_rows = FALSE,
    pvalue_fun = ~ style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 2)
  ) |>
  bold_labels() |>
  bold_p(t = 0.05) |>
  modify_header(estimate = "**OR**", p.value = "**P value**")
```

```{r}
tabla_7.2 <- glm(
  practica ~ edad.c + e_marital + ocupacion_convi + edad_relacion_sexual.c +
    num_hijos.c,
  data = data_uv,
  family = binomial(link = "logit") ) |>
  tbl_regression(
    exponentiate = TRUE,
    conf.int = TRUE,
    pvalue_fun = ~ style_pvalue(.x, digits = 3),
    estimate_fun = ~ style_number(.x, digits = 2)
  ) |>
  bold_p(t = 0.05) |>
  modify_header(estimate = "**OR**", 
                p.value = "**P value**")
```

### Merge tables

```{r}
table_7 =
  tbl_merge(tbls = 
              list(tabla_7.1, tabla_7.2), 
            tab_spanner = c("**Univariate analysis**",
                            "**Multivariate analysis**"))
```

```{r}
table_7 <- as_flex_table(table_7)
# Save tables
save_as_docx(table_7, path = "Table_7.docx", align = "center")
```